---
output:
  pdf_document: default
  html_document:
    df_print: paged
documentclass: report
geometry: margin=2cm
editor_options:
  chunk_output_type: console
---

```{r rmd setup, include=FALSE}
knitr::opts_chunk$set(echo    = FALSE,
                      cache   = FALSE,
                      message = FALSE)
options(knitr.kable.NA = "")
```

```{r global settings, include=FALSE}
# include model details (smooth effects, residual plots etc.)
model_details <- T
# response variables
response_vec <- c("TRT","FRT","RRT")
# define for which models the 'letters per word' effect should be estimated
# nonlinearly (default: all)
nonlinear_effect <- c("TRT","FRT","RRT") # set to c() to estimate all effects as linear effects
# complete remove the 'letters per word' effect in a model?
# Use case: Re-reading time models often show negligibly small effects, which
#           can lead to negative predicted values in the case of too many
#           zero observations. In these cases, removing the word effect makes sense.
no_effect <- c() # set to c("RRD") to remove the word effect for RRD
# AOI.conditions per model
AOIcond_list <- list(
  "Model1" = c(
    "CE0_1", "C1_1", "C2_1", "C3_1", "C4_1", "C5_1", "C6_1", "C7_1",
             "E1_1", "E2_1", "E3_1", "E4_1", "E5_1", "E6_1", "E7_1",
    "CE0_2", "C1_2", "C2_2", "C3_2", "C4_2", "C5_2", "C6_2", "C7_2",
             "E1_2", "E2_2", "E3_2", "E4_2", "E5_2", "E6_2", "E7_2",
             "C1_3", "C2_3", "C3_3", "C4_3", "C5_3", "C6_3", "C7_3",
             "E1_3", "E2_3", "E3_3", "E4_3", "E5_3", "E6_3", "E7_3",
    "CE0_4", "C1_4", "C2_4", "C3_4", "C4_4", "C5_4", "C6_4", "C7_4",
             "E1_4", "E2_4", "E3_4", "E4_4", "E5_4", "E6_4", "E7_4",
    "CE0_5", "C1_5", "C2_5", "C3_5", "C4_5", "C5_5", "C6_5", "C7_5",
             "E1_5", "E2_5", "E3_5", "E4_5", "E5_5", "E6_5", "E7_5",
             "C1_6", "C2_6", "C3_6", "C4_6", "C5_6", "C6_6", "C7_6",
             "E1_6", "E2_6", "E3_6", "E4_6", "E5_6", "E6_6", "E7_6",
    "CE0_7", "C1_7", "C2_7", "C3_7", "C4_7", "C5_7", "C6_7", "C7_7",
             "E1_7", "E2_7", "E3_7", "E4_7", "E5_7", "E6_7", "E7_7",
             "C1_8", "C2_8", "C3_8", "C4_8", "C5_8", "C6_8", "C7_8",
             "E1_8", "E2_8", "E3_8", "E4_8", "E5_8", "E6_8", "E7_8"
  ),
  "Model2" = c(
    "CE0_1", "C1_1", "C2_1", "C3_1", "C4_1", "C5_1", "C6_1", "C7_1",
    "CE0_2", "C1_2", "C2_2", "C3_2", "C4_2", "C5_2", "C6_2", "C7_2",
             "C1_3", "C2_3", "C3_3", "C4_3", "C5_3", "C6_3", "C7_3",
    "CE0_4", "C1_4", "C2_4", "C3_4", "C4_4", "C5_4", "C6_4", "C7_4",
    "CE0_5", "C1_5", "C2_5", "C3_5", "C4_5", "C5_5", "C6_5", "C7_5",
             "C1_6", "C2_6", "C3_6", "C4_6", "C5_6", "C6_6", "C7_6",
    "CE0_7", "C1_7", "C2_7", "C3_7", "C4_7", "C5_7", "C6_7", "C7_7",
             "C1_8", "C2_8", "C3_8", "C4_8", "C5_8", "C6_8", "C7_8"
  ),
  "Model3" = c(
    "CE0_1", "E1_1", "E2_1", "E3_1", "E4_1", "E5_1", "E6_1", "E7_1",
    "CE0_2", "E1_2", "E2_2", "E3_2", "E4_2", "E5_2", "E6_2", "E7_2",
             "E1_3", "E2_3", "E3_3", "E4_3", "E5_3", "E6_3", "E7_3",
    "CE0_4", "E1_4", "E2_4", "E3_4", "E4_4", "E5_4", "E6_4", "E7_4",
    "CE0_5", "E1_5", "E2_5", "E3_5", "E4_5", "E5_5", "E6_5", "E7_5",
             "E1_6", "E2_6", "E3_6", "E4_6", "E5_6", "E6_6", "E7_6",
    "CE0_7", "E1_7", "E2_7", "E3_7", "E4_7", "E5_7", "E6_7", "E7_7",
             "E1_8", "E2_8", "E3_8", "E4_8", "E5_8", "E6_8", "E7_8"
  )
)
### hypotheses, each comparing two AOI.conditions
# in case of no hypotheses at all: 'h_list <- NULL'
# in case of no hypotheses for model X: Simply create no list entry with name 'ModelX'
hypo_list <- NULL
```


\input{0_tex/1_titlepage}
\createTitlepage{Encapsulation \& Discursive Labels
}{Reading time \& Discourse particle analysis
}{ Helen Alber \\ Lisa Kleinlein
}

\input{0_tex/2_introduction}


```{r R setup, warning=FALSE, echo=FALSE}
# load packages
library(knitr)        # output table editing etc.
library(tidyverse)    # data management and ggplot2
library(DPKogHelpers) # Helper functions for the DPKog project
library(mgcv)         # Additive regression models
library(Hmisc)
library(emmeans)
theme_set(theme_bw()) # set global theme for ggplot2 plots

# define paths
path_prepData  <- "0_data/2_preparedData/"
path_resTables <- "2_resultFiles/tables/"
path_resImages <- "2_resultFiles/images/"
```


```{r read prepared data, echo=FALSE}
dat <- read.csv2(paste0(path_prepData, "data_prepared.csv"), fileEncoding = "utf-8")
dat_new <- read.csv2(paste0(path_prepData, "data_prepared.csv"), fileEncoding = "utf-8")
# calculate mean nLetters.WD
nLetters.WD <- round(mean(dat$nLetters.WD), 2)
# ensure that Participant and Topic are encoded as factor variables
dat <- dat %>%
  mutate(Participant = factor(Participant),
         Topic       = factor(Topic))
```

```{r further data preparation, echo=FALSE}
AOIcond_vec <- sort(unique(unlist(AOIcond_list)))
dat <- dat %>% filter(AOI.condition %in% AOIcond_vec) %>%
    mutate(AOI.condition = factor(AOI.condition, levels = AOIcond_vec))
```


\newpage
#### Letters per word (with the average letters per word as horizontal line)
```{r plot nLetters.WD, fig.height=4, echo=FALSE}
ggplot(dat[grepl("_(1|2)$",dat$AOI.condition), ], 
  aes(x = AOI.condition, y = nLetters.WD)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  ylab("Letters per word") +
  geom_hline(yintercept = nLetters.WD, lty = 2)

ggplot(dat[grepl("_(3|4)$",dat$AOI.condition), ],
  aes(x = AOI.condition, y = nLetters.WD)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  ylab("Letters per word") +
  geom_hline(yintercept = nLetters.WD, lty = 2)

ggplot(dat[grepl("_(5|6)$",dat$AOI.condition), ],
  aes(x = AOI.condition, y = nLetters.WD)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  ylab("Letters per word") +
  geom_hline(yintercept = nLetters.WD, lty = 2)
  
ggplot(dat[grepl("_(7|8)$",dat$AOI.condition), ],
  aes(x = AOI.condition, y = nLetters.WD)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
  ylab("Letters per word") +
  geom_hline(yintercept = nLetters.WD, lty = 2)
```

\newpage

#### Observations per AOI.condition
```{r table aoi.conditions, echo=FALSE}
freq <- sapply(AOIcond_vec, function(AOIcond) {
  length(unique(dat$observation[dat$AOI.condition == AOIcond]))
})
tab <- data.frame("AOI.condition" = AOIcond_vec,
                  "Freq" = unname(freq))
knitr::kable(tab)
```



\newpage
```{r model estimation, results = 'asis', cache = TRUE, echo=FALSE}
# In order to estimate the nLetters.WD effect as good as possible all AOI.conditions are thrown together into one big model.
# The following model_list contains this big model once for each specified model. Only if the intercept between
# two models differs, then the big model is reestimated.
model_list <- lapply(seq_len(length(AOIcond_list)), function(i) {
  m_list <- lapply(seq_len(length(response_vec)), function(j) {
    message(paste0("Estimate model ",i,"_",response_vec[j],"..."))
    # check if the current model has the same intercept as one of the previous models
    same_intercept_index <- ifelse(i == 1, NA, match(AOIcond_list[[i]][1], sapply(AOIcond_list[1:(i-1)], function(x) x[1])))
    # only reestimate the model if none was estimated before or if the intercept changed compared to previous models
    if (!is.na(same_intercept_index)) { # no reestimation necessary
      return(paste0(same_intercept_index,"_",j))
    } else { # estimation necessary
      dat_i <- dat %>% mutate(AOI.condition = relevel(AOI.condition, ref = AOIcond_list[[i]][1]))
      fm_covars <- "~ AOI.condition"
      if (!(response_vec[j] %in% no_effect)) { # add 'letters per word' effect
        if (response_vec[j] %in% nonlinear_effect) {
          fm_covars <- paste(fm_covars, "+ s(nLetters.WD, bs='ps', k = 4)")
        } else { # RRT and TRT
          fm_covars <- paste(fm_covars, "+ nLetters.WD")
        }
      }
      fm_covars <- paste(fm_covars, "+ s(Topic, bs='re') + s(Participant, bs='re')")
      fm <- as.formula(paste0(response_vec[j], ".WD", fm_covars))
      bam(fm, data = dat_i, method = "REML", nthreads = 10)
    }
  })
  names(m_list) <- response_vec
  m_list
})
names(model_list) <- paste0("Model", seq_len(length(model_list)))

# copy the models where no reestimation was necessary as of equal intercepts
if (length(model_list) > 1) {
  for (i in 2:length(model_list)) {
    for (j in 1:length(model_list[[i]])) {
      if (is.character(model_list[[i]][[j]])) {
        indices <- as.numeric(strsplit(model_list[[i]][[j]], "\\_")[[1]])
        model_list[[i]][[j]] <- model_list[[indices[1]]][[indices[2]]]
      }
    }
  }
}
```


```{r model details, results='asis', echo=FALSE}
# Smooth nLetters.WD effect and residual plot
if (model_details) {
  for (j in seq_len(length(response_vec))) {
    cat("\n\n\\newpage\n")
    m <- model_list[[1]][[j]]
        if (response_vec[j] %in% no_effect) {
      cat("The 'letters per word' effect was removed from the model after visual
          inspection since the effect was negligibly small.")
      cat("\n")
    } else if (response_vec[j] %in% nonlinear_effect) {
      plot(m, select = 1, main = paste0("Global ",response_vec[j]," model"), rug = TRUE)
    } else {
      cat("The 'letters per word' effect was estimated linearly after visual
          inspection of the nonlinear effect.\n\n\n")
      tab <- summary(m)$p.table
      tab <- round(tab[which(row.names(tab) == "nLetters.WD"),c(1,2,4)], 4)
      names(tab)[3] <- "p.value"
      print(knitr::kable(tab, col.names = "value"))
      cat("\n")
    }
    cat("\n\n\n\n\n\n\n")
    plot(m$fitted, m$residuals, main = paste0("Global ",response_vec[j]," model"), col = alpha("black", 0.05), pch = 19, cex = 0.5)
  }
  cat("\n\n\\newpage\n")
} else { # if no model details are shown, print a message on (non)linear Letters.WD effets
  if (length(nonlinear_effect) == 0) {
    if (length(no_effect) > 0)
      cat(paste0("The 'letters per word' effects were removed from the model(s) ",
                 paste(no_effect, collapse = ", ")," since they were negligibly small."))
    cat("All estimated 'letters per word' effects were estimated as linear effects.\n\n\\newpage\n")
  } else {
    if (length(no_effect) > 0) { # if the 'letters per word' was excluded in some model
      real_nonlinear_effect <- nonlinear_effect[!(nonlinear_effect %in% no_effect)]
      cat(paste0("The 'letters per word' effects were estimated as nonlinear effects
               in the model(s) ",paste(real_nonlinear_effect, collapse = ", "),
               ". The 'letters per word' effects were removed from the model(s) ",
               paste(no_effect, collapse = ", ")," since they were negligibly small.",
               " In all other models (if any) the effect was estimated as a linear effect.",
               "\n\n\\newpage\n"))
    } else { # if all models contained a 'letters per word' effect
      cat(paste0("The 'letters per word' effects were estimated as nonlinear effects
               in the model(s) ",paste(nonlinear_effect, collapse = ", "),
               ". In all other models the effect was estimated as a linear effect.",
               "\n\n\\newpage\n"))
    }
  }
}
```



```{r model results, results='asis', echo=FALSE}
for (i in seq_len(length(AOIcond_list))) {
  # retrieve the y limits for plotting over all response variables
  max_fitted <- sapply(model_list[[i]], function(model) { max(model$fitted.values[model$model$AOI.condition %in% AOIcond_list[[i]]]) })
  ylim <- c(0, max(max_fitted))
  
  for (j in seq_len(length(response_vec))) {
    # 1) Plot of model predictions
    res_list <- DPKogHelpers::plot_predictions(model = model_list[[i]][[j]],
                                               nLetters.WD = nLetters.WD,
                                               groups_vec = AOIcond_list[[i]],
                                               model_name = paste("Model",i),
                                               ylim = ylim,
                                               xlab_size = 2)
    ggsave(plot = res_list$plot, filename = paste0(path_resImages, "plot_m",i,"_", response_vec[j], ".pdf"), width = 8, height = 5)
    
    # 2) Table of estimates and model predictions
    print(knitr::kable(res_list$table))
    cat("\n") # necessary after printing a kable() in a for loop
    cat("\\newpage")
    write.csv(res_list$table, file = paste0(path_resTables, "tab_m",i,"_",response_vec[j],".csv"), row.names = TRUE)
  }
}
```

```{r checks, include=FALSE}
# Look at plot_predictions() function
# mean(as.numeric(unlist(dat[dat$AOI.condition == "C6_1", "RRT"])), na.rm = TRUE)

# C6_1 is whole CI, coreference and recategorizing
# mean(dat[dat$AOI.condition == "C6_1", ]$nWords)
# mean(dat[dat$AOI.condition == "C6_1", ]$RRT)
# median(dat[dat$AOI.condition == "C6_1", ]$RRT)

# Spaghetti-Plot: spaghettis are Participants, x-axis is the AOI.condition, y-axis is the rereading time (RRT) with ggplot, no legend:
# ggplot(dat[dat$AOI.condition %in% c("C3_1", "C4_1", "C5_1", "C6_1", "C7_1"), ], aes(x = AOI.condition, y = RRT, color = Participant, group = Participant)) +
#   geom_point(stat = "summary", fun = mean) +
#   geom_line(stat = "summary", fun = mean) +
#   theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 6)) +
#   theme(legend.position = "none")


# C6 & C7 only from one experiment, fewer data, reflected in higher standard error (see C1_6, also fewer data points, why?)
# estimate of C6 > C7
# --> change x-axis labels into better readability (model 1)
# --> C6 high variance between the AOIs

# dat_max <- dat %>%
#   group_by(AOI.condition) %>%
#   arrange(desc(RRT)) %>%  
#   slice_max(order_by = RRT, n = 10, with_ties = FALSE)
# 
# dat_max$AOI.condition <- factor(dat_max$AOI.condition)
# dat_max$condition <- factor(dat_max$condition)
# 
# ggplot(data = dat_max[dat_max$AOI == 1,], aes(x = condition, y = RRT.WD)) +
#   geom_point()
# 
# ggplot(data = dat[dat$AOI == 1,], aes(x = condition, y = RRT.WD)) +
#   geom_point()

# If there is a RRT.WD > 400ms, what is the TRT.WD then? Did outlier exclusion work?
#View(dat[dat$RRT.WD > 400, c("TRT.WD", "RRT.WD")])
#sum(dat$TRT.WD > 800)
#View(dat_new[dat_new$TRT.WD > 800, c("TRT.WD", "FRT.WD", "RRT.WD", "AOI")])
#View(dat_new[dat_new$TRT.WD > 800 & dat_new$AOI == 1, c("TRT.WD", "FRT.WD", "RRT.WD", "AOI")])
#View(dat_new[dat_new$observation %in% dat_new[dat_new$TRT.WD > 800, ]$observation, c("TRT.WD", "FRT.WD", "RRT.WD", "AOI")])
```

\newpage
### Second Model (AOI1)
```{r data 2, echo=FALSE}
dat$mechanism <- substr(dat$condition, 1, 1)
dat$mechanism[dat$condition == "CE0"] <- "none"
dat$info <- substr(dat$condition, 2, 2) 
dat$info[dat$condition == "CE0"] <- 0

# factors with desired level order
dat$mechanism <- factor(dat$mechanism)
dat$mechanism <- relevel(dat$mechanism, ref = "C")
dat$info <- factor(dat$info, levels = c("1", "2", "3", "4", "5", "6", "7", "0"))
dat$info_bin <- factor(ifelse(dat$info == "1", "pronominal", "lexical"),
                          levels = c("pronominal", "lexical"))


dat_mod2 <- dat[dat$AOI == 1,]

dat_mod2$TRT.L <- dat_mod2$TRT / dat_mod2$nLetters
dat_mod2$FRT.L <- dat_mod2$FRT / dat_mod2$nLetters
dat_mod2$RRT.L <- dat_mod2$RRT / dat_mod2$nLetters
```


```{r, echo=FALSE}
mod_TRT <- gam(data = dat_mod2,
               formula = TRT.L ~ mechanism + info +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_FRT <- gam(data = dat_mod2,
               formula = FRT.L ~ mechanism + info +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_RRT <- gam(data = dat_mod2,
               formula = RRT.L ~ mechanism + info +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))
```


```{r}
# newdat <- expand.grid(
#   mechanism = unique(dat_mod2$mechanism),
#   cond = unique(dat_mod2$cond)
# )
# 
# # random sample participant and topic (gets set to 0 for pred.)
# newdat$Participant <- sample(dat_mod2$Participant, nrow(newdat), replace = TRUE)
# newdat$Topic <- sample(dat_mod2$Topic, nrow(newdat), replace = TRUE)
# 
# fitted_values <- predict(mod_TRT, newdata = newdat, type = "response", exclude = c("s(Participant)","s(Topic)"))
# fitted_values
# 
# newdat2 <- newdat[c(22:24, seq(19, 1, -3)),]
# fitted_values2 <- predict(mod_TRT, newdata = newdat2, type = "response", exclude = c("s(Participant)","s(Topic)"))
# fitted_values2
```


```{r, results='asis', echo=FALSE}
names_res <- c("Estimates", "Std.Error", "p.value")

res_mod_TRT <- data.frame(cbind(round(summary(mod_TRT)$p.table[, c(1, 2, 4)], 4)))
res_mod_TRT <- rownames_to_column(res_mod_TRT, var = "TRT")
colnames(res_mod_TRT) <- c("TRT per Letter", names_res)

res_mod_FRT <- data.frame(cbind(round(summary(mod_FRT)$p.table[, c(1, 2, 4)], 4)))
res_mod_FRT <- rownames_to_column(res_mod_FRT, var = "FRT")
colnames(res_mod_FRT) <- c("FRT per Letter", names_res)

res_mod_RRT <- data.frame(cbind(round(summary(mod_RRT)$p.table[, c(1, 2, 4)], 4)))
res_mod_RRT <- rownames_to_column(res_mod_RRT, var = "RRT")
colnames(res_mod_RRT) <- c("RRT per Letter", names_res)

kable(res_mod_TRT)
kable(res_mod_FRT)
kable(res_mod_RRT)

rand_eff_message <- function(mod) {
  message <- c()
  if(all(summary(mod)$s.table[,4] < 0.05)) {
    message <- paste0("Both random effects, for ",
                      substr(names(summary(mod)$s.table[,4])[1], 3,
                             nchar(names(summary(mod)$s.table[,4])[1])-1),
                      " and ",
                      substr(names(summary(mod)$s.table[,4])[2], 3,
                             nchar(names(summary(mod)$s.table[,4])[2])-1),
                      ", are significant w.r.t alpha = 0.05.")
  } else {
    if(summary(mod)$s.table[1,4] < 0.05) {
      message <- paste0("The random effect ",
                        names(summary(mod)$s.table[,4])[1],
                        " is significant w.r.t alpha = 0.05.")
    } else if(summary(mod)$s.table[2,4] < 0.05) {
      message <- paste0("The random effect ",
                        names(summary(mod)$s.table[,4])[2],
                        " is significant w.r.t alpha = 0.05.")
    } else {
      message <- "No random effect is significant."
    }
  }
  return(message)
}

```

\newpage
```{r, echo=FALSE}
an_res_TRT <- round(anova.gam(mod_TRT)$pTerms.table, 4)
an_res_FRT <- round(anova.gam(mod_FRT)$pTerms.table, 4)
an_res_RRT <- round(anova.gam(mod_RRT)$pTerms.table, 4)
# kable(an_res_TRT)
# kable(an_res_FRT)
# kable(an_res_RRT)
```

For the TRT model: 
`r kable(an_res_TRT)`
`r rand_eff_message(mod_TRT)`

For the FRT model: 
`r kable(an_res_FRT)`
`r rand_eff_message(mod_FRT)`

For the RRT model: 
`r kable(an_res_RRT)`
`r rand_eff_message(mod_RRT)`


\newpage
Line plots for reading time over cond and separated by mechanism
\newline
Without and with confidence intervals
\newline
```{r, echo=FALSE, fig.width=3.5,fig.height=1.7}
par(mfrow = c(3, 2))
# TRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ],
       aes(x = info, y = TRT.L, color = mechanism, group = mechanism)) +
  geom_point(stat = "summary", fun = mean) +
  geom_line(stat = "summary", fun = mean) 

# TRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ], 
       aes(x = info, y = TRT.L, color = mechanism, group = mechanism)) +
  geom_point(stat = "summary", fun = mean) +
  geom_line(stat = "summary", fun = mean) +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1),
               geom = "errorbar", width = 0.2)

# FRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ],
       aes(x = info, y = FRT.L, color = mechanism, group = mechanism)) +
  geom_point(stat = "summary", fun = mean) +
  geom_line(stat = "summary", fun = mean)

# FRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ], 
       aes(x = info, y = FRT.L, color = mechanism, group = mechanism)) +
  geom_point(stat = "summary", fun = mean) +
  geom_line(stat = "summary", fun = mean) +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1),
               geom = "errorbar", width = 0.2)

# RRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ],
       aes(x = info, y = RRT.L, color = mechanism, group = mechanism)) +
  geom_point(stat = "summary", fun = mean) +
  geom_line(stat = "summary", fun = mean)

# RRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ], 
       aes(x = info, y = RRT.L, color = mechanism, group = mechanism)) +
  geom_point(stat = "summary", fun = mean) +
  geom_line(stat = "summary", fun = mean) +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1),
               geom = "errorbar", width = 0.2)
```



\newpage
Spaghetti plots (one line per person) for reading time over cond and separated by mechanism

```{r, echo=FALSE, fig.width=6,fig.height=3}
# TRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ],
       aes(x = info, y = TRT.L, group = RECORDING_SESSION_LABEL, color = mechanism)) +
  geom_line(alpha = 0.4) +
  theme_bw()
```
\newline
```{r, echo=FALSE, fig.width=6,fig.height=3}
# FRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ],
       aes(x = info, y = FRT.L, group = RECORDING_SESSION_LABEL, color = mechanism)) +
  geom_line(alpha = 0.4) +
  theme_bw()
```
\newline
```{r, echo=FALSE, fig.width=6,fig.height=3}
# RRT.L
ggplot(dat_mod2[dat_mod2$mechanism %in% c("C", "E"), ],
       aes(x = info, y = RRT.L, group = RECORDING_SESSION_LABEL, color = mechanism)) +
  geom_line(alpha = 0.4) +
  theme_bw()
```


\newpage
### Third Model (AOI1)
```{r model3, echo=FALSE}
dat_mod4 <- dat_mod2[!(dat_mod2$info == 0),]
```

```{r, echo=FALSE}
mod_TRT_bin <- gam(data = dat_mod4,
               formula = TRT.L ~ mechanism * info_bin +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_FRT_bin <- gam(data = dat_mod4,
               formula = FRT.L ~ mechanism * info_bin +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_RRT_bin <- gam(data = dat_mod4,
               formula = RRT.L ~ mechanism * info_bin +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))
```

```{r, results='asis', echo=FALSE}
res_mod_TRT_bin <- data.frame(cbind(round(summary(mod_TRT_bin)$p.table[, c(1, 2, 4)], 4)))
res_mod_TRT_bin <- rownames_to_column(res_mod_TRT_bin, var = "TRT")
colnames(res_mod_TRT_bin) <- c("TRT per Letter", names_res)

res_mod_FRT_bin <- data.frame(cbind(round(summary(mod_FRT_bin)$p.table[, c(1, 2, 4)], 4)))
res_mod_FRT_bin <- rownames_to_column(res_mod_FRT_bin, var = "FRT")
colnames(res_mod_FRT_bin) <- c("FRT per Letter", names_res)

res_mod_RRT_bin <- data.frame(cbind(round(summary(mod_RRT_bin)$p.table[, c(1, 2, 4)], 4)))
res_mod_RRT_bin <- rownames_to_column(res_mod_RRT_bin, var = "RRT")
colnames(res_mod_RRT_bin) <- c("RRT per Letter", names_res)

kable(res_mod_TRT_bin)
kable(res_mod_FRT_bin)
kable(res_mod_RRT_bin)
```

```{r pairwise, results='asis', echo=FALSE}
contrast_matrix <- list(
  "CP vs EP" = c(1, -1, 0, 0),
  "CP vs CL" = c(1, 0, -1, 0),
  "CL vs EL" = c(0, 0, 1, -1),
  "EP vs EL" = c(0, 1, 0, -1)
)
kable(as.data.frame(contrast(emmeans(mod_TRT_bin, specs = c("mechanism", "info_bin")), 
                             method = contrast_matrix)))
kable(as.data.frame(contrast(emmeans(mod_FRT_bin, specs = c("mechanism", "info_bin")), 
                             method = contrast_matrix)))
kable(as.data.frame(contrast(emmeans(mod_RRT_bin, specs = c("mechanism", "info_bin")),
                             method = contrast_matrix)))
```


\newpage
### Second Model (AOI6)
```{r, echo=FALSE}
dat_mod3 <- dat[dat$AOI == 6,]

dat_mod3$TRT.L <- dat_mod3$TRT / dat_mod3$nLetters
dat_mod3$FRT.L <- dat_mod3$FRT / dat_mod3$nLetters
dat_mod3$RRT.L <- dat_mod3$RRT / dat_mod3$nLetters

mod_TRT_6 <- gam(data = dat_mod3,
               formula = TRT.L ~ mechanism + info +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_FRT_6 <- gam(data = dat_mod3,
               formula = FRT.L ~ mechanism + info +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_RRT_6 <- gam(data = dat_mod3,
               formula = RRT.L ~ mechanism + info +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))
```

```{r, results='asis', echo=FALSE}
res_mod_TRT_6 <- data.frame(cbind(round(summary(mod_TRT_6)$p.table[, c(1, 2, 4)], 4)))
res_mod_TRT_6 <- rownames_to_column(res_mod_TRT_6, var = "TRT")
colnames(res_mod_TRT_6) <- c("TRT per Letter", names_res)

res_mod_FRT_6 <- data.frame(cbind(round(summary(mod_FRT_6)$p.table[, c(1, 2, 4)], 4)))
res_mod_FRT_6 <- rownames_to_column(res_mod_FRT_6, var = "FRT")
colnames(res_mod_FRT_6) <- c("FRT per Letter", names_res)

res_mod_RRT_6 <- data.frame(cbind(round(summary(mod_RRT_6)$p.table[, c(1, 2, 4)], 4)))
res_mod_RRT_6 <- rownames_to_column(res_mod_RRT_6, var = "RRT")
colnames(res_mod_RRT_6) <- c("RRT per Letter", names_res)

kable(res_mod_TRT_6)
kable(res_mod_FRT_6)
kable(res_mod_RRT_6)
```

\newpage
```{r, echo=FALSE}
an_res_TRT_6 <- round(anova.gam(mod_TRT_6)$pTerms.table, 4)
an_res_FRT_6 <- round(anova.gam(mod_FRT_6)$pTerms.table, 4)
an_res_RRT_6 <- round(anova.gam(mod_RRT_6)$pTerms.table, 4)
# kable(an_res_TRT)
# kable(an_res_FRT)
# kable(an_res_RRT)
```

For the TRT model: 
`r kable(an_res_TRT_6)`
`r rand_eff_message(mod_TRT_6)`

For the FRT model: 
`r kable(an_res_FRT_6)`
`r rand_eff_message(mod_FRT_6)`

For the RRT model: 
`r kable(an_res_RRT_6)`
`r rand_eff_message(mod_RRT_6)`

\newpage
### Third Model (AOI6)
```{r model3 AOI6, echo=FALSE}
dat_mod5 <- dat_mod3[!(dat_mod3$info == 0),]
```

```{r, echo=FALSE}
mod_TRT_bin_6 <- gam(data = dat_mod5,
               formula = TRT.L ~ mechanism * info_bin +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_FRT_bin_6 <- gam(data = dat_mod5,
               formula = FRT.L ~ mechanism * info_bin +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))

mod_RRT_bin_6 <- gam(data = dat_mod5,
               formula = RRT.L ~ mechanism * info_bin +
                 s(Participant, bs = "re") + s(Topic, bs = "re"))
```

```{r, results='asis', echo=FALSE}
res_mod_TRT_bin_6 <- data.frame(cbind(round(summary(mod_TRT_bin_6)$p.table[, c(1, 2, 4)], 4)))
res_mod_TRT_bin_6 <- rownames_to_column(res_mod_TRT_bin_6, var = "TRT")
colnames(res_mod_TRT_bin_6) <- c("TRT per Letter", names_res)

res_mod_FRT_bin_6 <- data.frame(cbind(round(summary(mod_FRT_bin_6)$p.table[, c(1, 2, 4)], 4)))
res_mod_FRT_bin_6 <- rownames_to_column(res_mod_FRT_bin_6, var = "FRT")
colnames(res_mod_FRT_bin_6) <- c("FRT per Letter", names_res)

res_mod_RRT_bin_6 <- data.frame(cbind(round(summary(mod_RRT_bin_6)$p.table[, c(1, 2, 4)], 4)))
res_mod_RRT_bin_6 <- rownames_to_column(res_mod_RRT_bin_6, var = "RRT")
colnames(res_mod_RRT_bin_6) <- c("RRT per Letter", names_res)

kable(res_mod_TRT_bin_6)
kable(res_mod_FRT_bin_6)
kable(res_mod_RRT_bin_6)
```

```{r pairwise6, results='asis', echo=FALSE}
kable(as.data.frame(contrast(emmeans(mod_TRT_bin_6, specs = c("mechanism", "info_bin")), 
                             method = contrast_matrix)))
kable(as.data.frame(contrast(emmeans(mod_FRT_bin_6, specs = c("mechanism", "info_bin")), 
                             method = contrast_matrix)))
kable(as.data.frame(contrast(emmeans(mod_RRT_bin_6, specs = c("mechanism", "info_bin")),
                             method = contrast_matrix)))
```

\newpage
### Hypothesis tests
```{r model results hypothesis tests, results='asis', echo=FALSE}
if (is.null(hypo_list)) {
  message <- "No hypothesis tests were performed"
} else if (!is.null(hypo_list)) {
  message <- c()
  for (i in seq_len(length(AOIcond_list))) {
    cat(paste0("#### ",names(AOIcond_list)[i]))
    if (names(AOIcond_list)[i] %in% names(hypo_list)) {
      hypo_index <- match(names(AOIcond_list)[i], names(hypo_list))
      # Results table for hypothesis tests
      p <- DPKogHelpers::create_pTable(model_list = model_list[[i]],
                                       hypo_vec = hypo_list[[hypo_index]],
                                       holm_correction = TRUE)
      print(knitr::kable(p$pTable))
      cat("\n") # necessary after printing a kable() in a for loop
      cat(paste0(p$info,"\n\n"))
      write.csv(p$pTable, file = paste0(path_resTables, "pTab_m",i,".csv"), row.names = TRUE)
    } else {
      cat("\nNo hypotheses were tested\n\n")
    }
  }
}
```
<!-- print the messages -->
`r DPKogHelpers::print_rmdMessages(message, title = NULL)`

